Sperm do not evolve to collaborate in female meiotic drive.

### 2014-05-14 writeup_and_notes/male_dependent_drive.tex
made invasion of unlinked mod an equation and pointed to it in main text

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppression can. 
%	that is sperm-acting alleles that act to restore  fairness of female meiosis, can. %If these sperm-acting drive suppressors arise on
If a sperm-acting allele that restores fairness to female meiosis arises on
	the non-driving $A$ background (creating a third allele $A^{-}$), 
	or is unlinked to the drive locus, it readily invades a population segregating
	for the drive system ($AB$, see Figure and \yb{Equations \ref{A-}).} %still coming together 
This allele lowers the frequency of the original drive system (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.

@@

\subsubsection*{Model 6. Unlinked drive-modifier:}
For the unlinked, model we introduce another locus where drive is modified in A/B females fertilized by $F$ allele, 
	while the wild-type $E$ does not influence drive. 
Assuming HWE and linkage equilibrium, an $F$ allele increases in frequency when 
	$-\epsilon f_A f_B (f_B s + s_h (fA - fB) ) >0$, corresponding to any level of drive suppression ($\epsilon<0$) 
	when the the fitness cost of the driver does not display over- or under-dominance. 
Notably, this result holds while assuming complete linkage equilibrium, and therefore sperm suppression of female meiotic drive is likely more powerful than female enforced systems which usually spread due to the indirect benefit of avoiding drive haplotypes \citep[e.g. ][]{Brandvain2012}.  
The spread of this driver does not, however, depend on assumption of HWE, and linkage equilibrium - exact results resemble analytical approximations. 
%\paragraph{three allele system}
%$x_{AA}$, $x_{AB}$,$x_{AB'}$, $w_{BB'} x_{BB'}$, $w_{B'B'} x_{BB}$, $w_{B'B'} x_{B'B'}$
%We denote the frequency of the three genotypes in the population at birth are
%$x_{AA}$, $x_{AB}$, $x_{AB'}$, $x_{BB'}$, $x_{BB}$, $x_{B'B'}$. 
%The mean relative fitness of the population is 
%\begin{equation}
%x_{AA}+x_{AB}+ x_{AB'}+ w_{BB'} +x_{BB'}+w_{B'B'}x_{BB} + w_{B'B'} x_{B'B'} 
%\end{equation}
%The frequency of the genotypes in meiotic-cells of female adults is 
%\begin{equation}
%\frac{1}{\bar{w}}\Big( x_{AA}, ~x_{AB},~ x_{AB'},~ w_{BB'} x_{BB'},~ w_{B'B'}x_{BB},
%~w_{B'B'} x_{B'B'} \Big)
%\end{equation}
%The frequency of fertilization events can be found by combining these
%female frequencies with the frequency of the three alleles in sperm is
%\begin{eqnarray}
%x_A = & x_{AA} + \frac{1}{2} x_{AB}+ \frac{1}{2} x_{AB'} \\
%x_B = & w_{BB}  x_{BB} +   w_{BB'} \frac{1}{2} x_{BB'}+ \frac{1}{2} x_{AB} \\
%x_{B'} = & w_{B'B'}  x_{B'B'} +   w_{BB'} \frac{1}{2} + x_{BB'}+ \frac{1}{2} x_{AB'}  
%\end{eqnarray}
%in combination with the transmission probabilities given in Figure
%\ref{Eggsperm_3_allele_cartoon}A.

>>>>

%%%sperm-acting drive suppressors
While  sperm enhancement of a female drive cannot displace a polymorphic female driver, sperm based drive suppression can. 
%	that is sperm-acting alleles that act to restore  fairness of female meiosis, can. %If these sperm-acting drive suppressors arise on
If a sperm-acting allele that restores fairness to female meiosis arises on
	the non-driving $A$ background (creating a third allele $A^{-}$), 
	or is unlinked to the drive locus, it readily invades a population segregating
	for the drive system ($AB$, see Figure and Equations \ref{A-} and \ref{unlinked}).  
This allele lowers the frequency of the original drive system (perhaps to zero),
	and spreads to fixation if it does not carry strong fitness costs
	(Figure \ref{Eggsperm_3_allele_cartoon} and \ref{Trajectories_of_supressors}A). 
This result is consistent with previous work showing that drive suppressors unlinked to, or in repulsion phase with drivers usually invade polymorphic drive systems \citep[e.g. ][]{Brandvain2012}.

@@

\subsubsection*{Model 6. Unlinked drive-modifier:}
For the unlinked, model we introduce another locus where drive is modified in A/B females fertilized by $F$ allele, 
	while the wild-type $E$ does not influence drive. 
Assuming HWE and linkage equilibrium, the change in frequency of a rare unlinked, sperm-acting drive modifier is 
\begin{equation} \Delta F =-\epsilon f_A f_B (f_B s + s_h (fA - fB) ) \frac{f_F}{\bar{w}}  \label{unlinked} \end{equation}
% an $F$ allele increases in frequency when 
%	$-\epsilon f_A f_B (f_B s + s_h (fA - fB) ) >0$, corresponding to any level of drive suppression ($\epsilon<0$) 
Thus, a rare drive suppressor ($\epsilon<0$) will spread so long as  the fitness cost of the driver does not display over- or under-dominance. 
Notably, this result holds while assuming complete linkage equilibrium, and therefore sperm suppression of female meiotic drive is likely more powerful than female enforced systems which usually spread due to the indirect benefit of avoiding drive haplotypes \citep[e.g. ][]{Brandvain2012}.  
The spread of this driver does not, however, depend on assumption of HWE, and linkage equilibrium - exact results resemble analytical approximations. 
%\paragraph{three allele system}
%$x_{AA}$, $x_{AB}$,$x_{AB'}$, $w_{BB'} x_{BB'}$, $w_{B'B'} x_{BB}$, $w_{B'B'} x_{B'B'}$
%We denote the frequency of the three genotypes in the population at birth are
%$x_{AA}$, $x_{AB}$, $x_{AB'}$, $x_{BB'}$, $x_{BB}$, $x_{B'B'}$. 
%The mean relative fitness of the population is 
%\begin{equation}
%x_{AA}+x_{AB}+ x_{AB'}+ w_{BB'} +x_{BB'}+w_{B'B'}x_{BB} + w_{B'B'} x_{B'B'} 
%\end{equation}
%The frequency of the genotypes in meiotic-cells of female adults is 
%\begin{equation}
%\frac{1}{\bar{w}}\Big( x_{AA}, ~x_{AB},~ x_{AB'},~ w_{BB'} x_{BB'},~ w_{B'B'}x_{BB},
%~w_{B'B'} x_{B'B'} \Big)
%\end{equation}
%The frequency of fertilization events can be found by combining these
%female frequencies with the frequency of the three alleles in sperm is
%\begin{eqnarray}
%x_A = & x_{AA} + \frac{1}{2} x_{AB}+ \frac{1}{2} x_{AB'} \\
%x_B = & w_{BB}  x_{BB} +   w_{BB'} \frac{1}{2} x_{BB'}+ \frac{1}{2} x_{AB} \\
%x_{B'} = & w_{B'B'}  x_{B'B'} +   w_{BB'} \frac{1}{2} + x_{BB'}+ \frac{1}{2} x_{AB'}  
%\end{eqnarray}
%in combination with the transmission probabilities given in Figure
%\ref{Eggsperm_3_allele_cartoon}A.
